\newtheorem{theo}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{col}{Corollary}
\newtheorem{defini}{Definition}
\newtheorem{pro}{Property}
\def\bm#1{\mbox{\boldmath{$#1$}}}
\def\eqtri{\stackrel{\triangle}{=}}
\def\c#1{#1^{\dagger}}
\newcommand{\gf}{\mbox{$GF(q)$}}
\newcommand{\av}[1]{\mbox{E${\displaystyle\left[ #1 \right]}$}}
\def\r{\bm{r}}
\def\s{\bm{s}}
\def\w{\bm{w}}
\def\x{\bm{x}}
\def\y{\bm{y}}
\def\a{\bm{a}}
\def\u{\bm{u}}
\def\cX{{\cal X}}
\def\cY{{\cal Y}}
\def\cP{{\cal P}}
\def\cV{{\cal V}}
\newcommand{\g}{\mbox{$\Gamma$}}
\def\qed{\strut\hfill(Q.E.D.)}
\def\eot{\strut\hfill$\Box$}
\def\osum{\bigcirc\hspace{-1.2em}\sum}
\newcommand{\vt}[1]{\mbox{\boldmath $#1$}}

\chapter{Introduction}
The problem of specifying the structure of codes which achieve
Gallager's error exponent remains as a major problem
in information theory and coding theory.
On this subject, Thommesen\cite{th} investigated the concatenated codes with
maximum distance separable (MDS) 
outer codes and time-varying inner codes used on DMC with
maximum likelihood decoding. He has proved that Gallager's error
exponents are asymptotically obtained for all rates by such codes.
On the other hand, Ahlswede and Dueck\cite{ah} investigated the code 
called ``permutation code'' obtained by 
permutating coordinates of a single codeword.
They have proved that Gallager's error exponents 
are asymptotically obtained for all rates less than capacity,
by employing maximum mutual information (MMI) decoding. 
Since both encoding and decoding of 
their codes do not depend on particular channel,
and their codes yield the best asymptotic performance,
they are usually called as ``universal codes''.
However, it is not known whether universal codes can be
obtained by other structures of codes.

This paper extends the results of Thommesen, and shows 
that there exist good universal codes in a class of concatenated codes.
We investigate the decoding error probability of concatenated codes 
employing MDS codes as outer codes and time-varying randomly selected 
constant composition codes as inner codes, 
used on arbitrary DMC with modified MMI decoding.
It is shown that Gallager's 
error exponents are universally obtained for all rates
by the proposed codes, provided that the length of the code
is sufficiently large.

