\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}
\bibitem{fo} G. D. Forney, Jr. : ``Concatenated Codes'', MIT Press (1966).
%
\bibitem{ju} J. Justesen : ``A Class of Constructive Asymptotically Good
Algebraic Codes'', IEEE Trans. on Inform. Theory, vol.IT-18, no.5, 
 pp.652-656 (Sep. 1972).
%
\bibitem{dp} P. Delsarte and P. Piret :``Algebraic Constructions of Shannon
Codes for Regular Channel'', IEEE Trans. on Inform. Theory, vol.IT-28, no.4,
pp.593-599 (July 1982).
%
\bibitem{st} M. Steiner : ``Constructive Codes for Arbitrary Discrete 
Memoryless Channels'', IEEE Trans. on Inform. Theory, vol.IT-40,
no.3, pp.929-934 (May 1994).
%
\bibitem{go} V. D. Goppa : ``Codes on Algebraic Curves'', Soviet Math. Dokl. 
vol.24, pp.170-172 (1981).
%
\bibitem{uy} T. Uyematsu and E. Okamoto: ``A Construction of Codes 
with Exponential Error Bounds on Arbitrary Discrete Memoryless Channels'',
submitted to IEEE Trans. on Inform. Theory.
%
\bibitem{ga} R. G. Gallager : 
``Information Theory and Reliable Communication'', Wiley (1968).
%
\bibitem{th}C. Thommesen :
``Error-Correcting Capabilities of Concatenated Codes
with MDS Outer Codes on Memoryless Channels with Maximum-Likelihood Decoding'',
 IEEE Trans. Inform. Theory, vol. IT-33, no.5, pp. 632-640 (Sep. 1987).
%
\bibitem{ah}R.~Ahlswede and G.~Dueck: ``Good Codes Can Be Produced by a Few
Permutations'', IEEE Trans. on Inform. Theory, vol.IT-28,
no.3, pp.430-443 (May 1982).
%
\bibitem{ck} I.~Csisz\'{a}r and J.~K\"{o}rner: Information Theory, 
Coding Theorems for Discrete Memoryless Systems, Academic Press (1981).

\end{thebibliography}