
% \strut
% \vspace{20pt}

\renewcommand{\nomname}{PUBLICATIONS}
\markboth{\nomname}{\nomname}
% \noindent{\LARGE\bf Publications}


% \vspace{20pt}
\phantomsection\addcontentsline{toc}{chapter}{Publications}

\begin{publication}
\item[] \hspace{-1cm}{\LARGE\bf Journals} \\ 

\item 
B. T. Atmaja and M. Akagi, ``Dimensional speech emotion recognition from speech
features and word embeddings by using multitask learning," APSIPA Trans. Signal
Inf. Process., Vol. 9, No. May, p. e17, May 2020.

\item
R. Elbarougy, B.T. Atmaja and M. Akagi, ``Continuous Audiovisual Emotion
Recognition Using Feature Selection and LSTM,'' Journal of Signal Processing,
Vol. 24, No. 6, November 2020, pp. 229-235. 

\item
B.T. Atmaja and M. Akagi, ``Two-stage dimensional emotion recognition by fusing
predictions of acoustic and text networks using SVM,'' Speech Communication,
vol 126, February 2021, pp 9-21.
\verb|doi:10.1016/j.specom.2020.11.003|. \\

\item[] \hspace{-1cm}{\LARGE\bf International Conferences} \\ 

\item 
B.T. Atmaja, K. Shirai, and M. Akagi, ``Deep Learning-based Categorical and
Dimensional Emotion Recognition for Written and Spoken Text,''
\textit{International Seminar on Science and Technology}, Surabaya, 2019.

\item 
B. T. Atmaja, K. Shirai, and M. Akagi, ``Speech Emotion Recognition Using
Speech Feature and Word Embedding," in 2019 Asia-Pacific Signal and Information
Processing Association Annual Summit and Conference (APSIPA ASC), 2019, pp.
519--523.

\item
B. T. Atmaja and M. Akagi, ``Speech Emotion Recognition Based on Speech Segment
Using LSTM with Attention Model," in 2019 IEEE International Conference on
Signals and Systems (ICSigSys), 2019, pp. 40--44.

\item
B. T. Atmaja and M. Akagi, ``Multitask Learning and Multistage Fusion for Dimensional Audiovisual Emotion Recognition," in ICASSP 2020 - 2020 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2020, pp. 4482--4486.

\item
B. T. Atmaja and M. Akagi, ``The Effect of Silence Feature in Dimensional
Speech Emotion Recognition," in 10th International Conference on Speech Prosody
2020, 2020, May, pp. 26--30.

\item
B.T. Atmaja and M. Akagi, ``Improving Valence Prediction in
Dimensional Speech Emotion Recognition Using Linguistic Information, " in 2020
23nd Conference of the Oriental COCOSDA International Committee for the
Co-ordination and Standardisation of Speech Databases and Assessment Techniques
(O-COCOSDA), pp. 166-171. IEEE, 2020. [\textbf{Awarded as best student paper}]

\item
B.T. Atmaja and M. Akagi, ``On The Differences Between Song and Speech Emotion
Recognition: Effect of Feature Sets, Feature Types, and Classifiers'', TENCON
2020 - 2020 IEEE Region 10 Conference (TENCON), Osaka, Japan, 2020, pp. 968-972.

\item
B.T. Atmaja, Y. Hamada  and M. Akagi, ``Predicting Valence and Arousal by Aggregating Acoustic Features for Acoustic-Linguistic Information Fusion''
TENCON 2020 - 2020 IEEE Region 10 Conference (TENCON), Osaka, Japan, 2020, pp. 1081-1085. 

\item 
B.T. Atmaja and M. Akagi, ``Deep Multilayer Perceptrons for Dimensional Speech
Emotion Recognition,'' in 2020 Asia-Pacific Signal and Information Processing
Association Annual Summit and Conference (APSIPA ASC), Auckland, New Zealand,
2020, pp. 325-331.

\item 
B.T. Atmaja and M. Akagi, ``Evaluation of Error and Correlation-based Loss
Functions For Multitask Learning Dimensional Speech Emotion Recognition,''
International Conference on Acoustic and Vibration, Bali, Indonesia, 2020.
[\textbf{Awarded as best student paper and presentation}]\\

\item[] \hspace{-1cm}{\LARGE\bf Domestic Conferences} \\ 
\item 
R. Elbarougy, B.T. Atmaja, and M. Akagi, ``Continuous Tracking of Emotional
State from Speech Based on Emotion Unit,''\textit{In Proceeding ASJ Autumn
Meeting}, 2018.

\item
B.T. Atmaja, A.N.F. Fandy, D. Arifianto, and M. Akagi, ``Speech recognition on
Indonesian language by using time delay neural network,'' \textit{In Proceeding
ASJ Spring Meeting}, 2019, pp. 1291--1294.

\item
B.T. Atmaja, R. Elbarougy, and M. Akagi, ``RNN-based dimensional speech emotion
recognition,'' \textit{In Proceeding ASJ Autumn Meeting}, 2019, pp. 743--744.

\item
B.T. Atmaja and M. Akagi, ``Dimensional Speech Emotion Recognition from
Acoustic and Text Features Using Multitask Learning,'' \textit{In Proceeding
ASJ Spring Meeting}, 2020, pp. 1003--1004.

\end{publication}
